### 2018-11-02 Sabanci_talk/Sabanci_talk.tex
Slides, paper minor

\begin{frame}{Binary Neutron Star Inspirals}{Inspiral time}
Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
\\
\vspace{1mm}
Fix integration constant $\tau = t_\text{coal} - t >0$. \\
\vspace{2mm}
Introduce \red{inspiral time}, i.e, time to BNS \bl{coal}escence
%
\begin{align}
 \red{\tau_\text{insp}(f)} &= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
 &\simeq \red{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,\red{\left(\f{10\,\text{Hz}}{f}\right)^{8/3}\quad(2)}\nn
\end{align}
Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim f^{-5/3}$ %$\int df {f}/\dot{f}$
\begin{align}
 \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
 &\approx 1.605\times \red{10^4 \left(\f{10\,\text{Hz}}{f} \right)^{5/3}}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\quad \red{(3)}\nn
\end{align}
%
\begin{tikzpicture}[overlay,remember picture]
\node[draw, red,thick,minimum width=8.2cm,minimum height=1.3cm] (b) at (7.,3.35){};
\node[draw, red,thick,minimum width=10cm,minimum height=1.3cm] (b) at (6.2,1){};
\end{tikzpicture}
%
\end{frame}

@@

\begin{frame}{Supplement 1: mode suppression}
\begin{itemize}
 \item For $q=1$ due to symmetry only (2,2), (3,2), (4,2), (4,4) are nonzero 
 \item For $q\ne 1$ all $\ell \ge 2$ modes exist, but are much smaller than $(2,2)$
\end{itemize}

>>>>

\begin{frame}{Binary Neutron Star Inspirals}{\todo{Add $r(t)$ plot? }}
Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
\\
\vspace{1mm}
Fix integration constant $\tau = t_\text{coal} - t >0$. \\
\vspace{2mm}
Introduce \red{inspiral time}, i.e, time to BNS \bl{coal}escence
%
\begin{align}
 \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
 &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,\red{\left(\f{10\,\text{Hz}}{f}\right)^{8/3}\quad(2)}\nn
\end{align}
Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim \red{f^{-5/3}}$ %$\int df {f}/\dot{f}$
\begin{align}
 \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
 &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\red{ \left(\f{10\,\text{Hz}}{f} \right)^{5/3}}\quad \red{(3)}\nn
\end{align}
%
\begin{tikzpicture}[overlay,remember picture]
\node[draw, red,thick,minimum width=8.2cm,minimum height=1.3cm] (b) at (7.,3.35){};
\node[draw, red,thick,minimum width=10cm,minimum height=1.3cm] (b) at (6.2,1){};
\end{tikzpicture}
%
\[ 
\tfrac{\dot{r}}{r}\sim \tfrac{\dot{f}}{f} \Longrightarrow \red{r(\tau)}=r_i \left(\f{\red{\tau}}{\tau_i}\right)^{\red{1/4}}
\]

@@

\begin{frame}{Supplement 1: mode suppression}
\begin{itemize}
 \item For $q=1$ due to symmetry only (2,2), (3,2), (4,2), (4,4) are nonzero 
 \item For $q\ne 1$ all $\ell \ge 2$ modes exist, but are much smaller than $(2,2)$
\end{itemize}
\end{frame}

\begin{frame}{Supplement 2: The expression for $h_c(t)$}
Maggiore chapters 1, 3 and 4
\begin{itemize}
 \item Eq. (3.3) expanded to (3.9), (3.14) to (3.34) to (3.55) to (3.59)
 \item Eq. (3.72): $h(t)$ as angular distribution with mass moments $\ddot{M}_{ij}$'s
 \item At that point we get the scaling $h \sim \tfrac{1}{D}\tfrac{G}{c^4}\ddot{Q}_{ij}$.
 \item Eq. (3.275) shows it expanded in tensor harmonics so up to $\partial^2 Y^{\ell m}$
\end{itemize}

\begin{frame}{Supplement 3: Direction of GW emission}
 Mostly off the orbital plane and slightly forward
 \begin{itemize}
  \item Eqs. (3.337-3.338) and Fig. 3.7 show that $\tfrac{d\dot{E}}{d\Omega}$ is max at the poles
  \item Eqs. (4.347), (4.348) with Fig. 4.24 (page 228) show that even for $v=0.99$ the beaming
  is much less significant compared to EM beaming shown in Fig. 4.23.
 \end{itemize}
